Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-09-21 paper/paper.Rmd
Close #4 and add detail on GitHub actions compute

Our forecasts have performed relatively well compared to the majority of other submitted forecasts, but rarely outperforming significantly.
The model-based forecasts we have contributed have focussed on trying to carefully model the underlying infectious disease dynamics from infection through to symptom onset, and test positivity using non-exponential delay distributions whilst also attempting to model the complexity of daily, within the week, reporting periodicity [@REF].
Based on our observations our forecasts have generally captured changes in trend better than most submitted models that do not use human insight based on known policy changes, but have not been robust to reporting issues such as large outliers in reporting and changes to reporting patterns. 
Our previous methodology also requires significant computational resources running for an hour on a 16-core machine when producing forecasts for the European forecasting hub. 
In our model-based forecasts, we did not attempt to capture potential future interventions or known interventions not currently observed in the epidemiological data whereas in our human insight models these were implicitly included.
We found that our human insight-based forecasts significantly outperformed our model-based forecasts and hypothesised that this may have been driven by including additional information not observed in the epidemiological data [@REF]. 
Unlike our epidemiologically motivated forecast submissions, the hub ensemble forecasts were typically robust to daily reporting artefacts. They also demonstrated some ability to forecast future changes in trends that were not present in the observed data similarly to our human insight forecasts indicating the likely inclusion of either human insight, or assumptions about future interventions. 
In general, the ensemble forecasts were more auto-correlated and less reactive to changes from stable or reducing case incidence to increasing incidence. On the other hand, this also meant that the ensemble was less likely to adopt short-term changes in incidence and hence produced better long-term forecasts. Finally, the ensemble forecast tended to produce sharper forecasts and have a tendency towards under vs over predicting. There is some suggestion that this was partially driven by the ensemble forecast having non-exponential uncertainty, unlike many infectious disease forecasting models.

@@

To ensure the reproducibility of this analysis dependencies are managed using the `renv` R package (`0.14.0`) [@renv] and a Dockerfile file along with a built Docker image [@Boettiger:2015dw] (via GitHub Actions) is provided in the code repository.
Weekly forecasts are also made using `renv` and GitHub actions to ensure they require limited compute and that our implementation is independent of local resources facilitating democratised access.
The code for this analysis can be found here: https://github.com/epiforecasts/simplified-forecaster-evaluation
The code for the forecasting model defined above along with the infrastructure required to forecast using GitHub Actions can be found here: https://github.com/seabbs/ecdc-weekly-growth-forecasts
Versions archived on Zenodo are available [@REF] and [@REF].

@@

Whilst we derived our surrogate model from a range of assumptions based on observing ensemble forecasts behaviour and the behaviour and structure of submitted models this was by no means as structured or complete a process as it could have been.
In follow-up work, a more rigorous approach to this could be taken to further refine this set of assumptions, in particular using the input of a wider pool of researchers. 
The findings from our study may also be useful for informing this improved set of assumptions. 
In addition, the model we derived based on our assumptions was likely not optimal both in terms of compute time and accuracy at reproducing ensemble-like behaviour.
Models with a more complex auto-correlation structure and more refined approaches to localised trends should be explored to improve relative performance to ensemble forecasts.
An example of a family of possible approaches are structural time series models which have many of the characteristics implied by our assumptions for how forecast ensembles typically operate.
As we identified that the tails of our predictive distributions were responsible for a large proportion of the difference in performance compared to the forecast ensemble it may be the case that post-processing of forecasts from our surrogate model would enhance their similarity to the forecast ensemble.
This seems likely to improve out-of-sample performance but does not help with the secondary aim of understanding the implicit assumptions driving the performance of multi-model, multi-team infectious disease forecast ensembles.
As we have hypothesised that the use of absolute scoring measures is inappropriate and leads to performance characteristics that are unlikely to be favoured by forecast stakeholders more work should be done in this area.
If new forecast ensemble methods are adopted as best practice by forecast hubs then follow-up work attempting to create surrogate forecast models should also use these approaches and this will likely alter the observed characteristics of the hub ensemble forecasts, for example, the tendency to be poorly calibrated.
Lastly, here we have only explored a surrogate for an ensemble for a single disease, a limited set of locations, and a single target (incident cases), meaning our findings are difficult to generalise.
Follow-up work should explore whether this behaviour holds across diseases, locations, and epidemiological targets where the behaviour of ensembles is notably different [@REF].
However, this work is limited by the lack of large-scale forecast ensembling projects despite them showing obvious promise to improve the forecasts available to stakeholders.

>>>>

Our forecasts have performed relatively well compared to the majority of other submitted forecasts, but rarely outperforming significantly.
The model-based forecasts we have contributed have focussed on trying to carefully model the underlying infectious disease dynamics from infection through to symptom onset, and test positivity using non-exponential delay distributions whilst also attempting to model the complexity of daily, within the week, reporting periodicity [@REF].
Based on our observations our forecasts have generally captured changes in trend better than most submitted models that do not use human insight based on known policy changes, but have not been robust to reporting issues such as large outliers in reporting and changes to reporting patterns. 
Our previous methodology also requires significant computational resources running for an hour on a Azure D v5-series 16-core machine when producing forecasts for the European forecasting hub [@AzurePricing]. 
In our model-based forecasts, we did not attempt to capture potential future interventions or known interventions not currently observed in the epidemiological data whereas in our human insight models these were implicitly included.
We found that our human insight-based forecasts significantly outperformed our model-based forecasts and hypothesised that this may have been driven by including additional information not observed in the epidemiological data [@REF]. 
Unlike our epidemiologically motivated forecast submissions, the hub ensemble forecasts were typically robust to daily reporting artefacts. They also demonstrated some ability to forecast future changes in trends that were not present in the observed data similarly to our human insight forecasts indicating the likely inclusion of either human insight, or assumptions about future interventions. 
In general, the ensemble forecasts were more auto-correlated and less reactive to changes from stable or reducing case incidence to increasing incidence. On the other hand, this also meant that the ensemble was less likely to adopt short-term changes in incidence and hence produced better long-term forecasts. Finally, the ensemble forecast tended to produce sharper forecasts and have a tendency towards under vs over predicting. There is some suggestion that this was partially driven by the ensemble forecast having non-exponential uncertainty, unlike many infectious disease forecasting models.

@@

To ensure the reproducibility of this analysis dependencies are managed using the `renv` R package (`0.14.0`) [@renv] and a Dockerfile file along with a built Docker image [@Boettiger:2015dw] (via GitHub Actions [@GitHubActionsAbout]) is provided in the code repository.
Weekly forecasts were made using `renv` and based GitHub Actions free tier as available in 2022 to ensure they require limited compute and that our implementation is independent of local resources facilitating democratised access.
The free GitHub Actions runner we used for all forecasts was Ubuntu `20.04` based with 2 cores (x86_64), 7 GB of RAM, and 14 GB of SSD space.
The code for this analysis can be found here: https://github.com/epiforecasts/simplified-forecaster-evaluation
The code for the forecasting model defined above along with the infrastructure required to forecast using GitHub Actions can be found here: https://github.com/seabbs/ecdc-weekly-growth-forecasts
Versions archived on Zenodo are available [@REF] and [@REF].

@@

Whilst we derived our surrogate model from a range of assumptions based on observing ensemble forecasts behaviour and the behaviour and structure of submitted models this was by no means as structured or complete a process as it could have been.
In follow-up work, a more rigorous approach to this could be taken to further refine this set of assumptions, in particular using the input of a wider pool of researchers. 
The findings from our study may also be useful for informing this improved set of assumptions. 
In addition, the model we derived based on our assumptions was likely not optimal both in terms of compute time and accuracy at reproducing ensemble-like behaviour.
Models with a more complex auto-correlation structure and more refined approaches to localised trends should be explored to improve relative performance to ensemble forecasts.
An example of a family of possible approaches are structural time series models which have many of the characteristics implied by our assumptions for how forecast ensembles typically operate.
As we identified that the tails of our predictive distributions were responsible for a large proportion of the difference in performance compared to the forecast ensemble it may be the case that post-processing of forecasts from our surrogate model would enhance their similarity to the forecast ensemble.
This seems likely to improve out-of-sample performance but does not help with the secondary aim of understanding the implicit assumptions driving the performance of multi-model, multi-team infectious disease forecast ensembles.
As we have hypothesised that the use of absolute scoring measures is inappropriate and leads to performance characteristics that are unlikely to be favoured by forecast stakeholders more work should be done in this area.
If new forecast ensemble methods are adopted as best practice by forecast hubs then follow-up work attempting to create surrogate forecast models should also use these approaches and this will likely alter the observed characteristics of the hub ensemble forecasts, for example, the tendency to be poorly calibrated.
In September 2022, GitHub announced support for hosted GitHub Action runners with additional compute power [@GitHubActionsLargeRunners]. Whilst a paid feature this may allow more compute attensive models, with fewer potental performance trade-offs, to be easily democratised though only if funds are available to support the hosting costs.
One potential research area is to explore forecasting methods that can be used with a range of compute resources though this would require extensive evaluation and documentation to make it clear to users what the trade-offs between compute usage and forecast performance are.
Lastly, here we have only explored a surrogate for an ensemble for a single disease, a limited set of locations, and a single target (incident cases), meaning our findings are difficult to generalise.
Follow-up work should explore whether this behaviour holds across diseases, locations, and epidemiological targets where the behaviour of ensembles is notably different [@REF].
However, this work is limited by the lack of large-scale forecast ensembling projects despite them showing obvious promise to improve the forecasts available to stakeholders.
